\documentclass[12pt]{article}
\usepackage{fancyhdr}
\usepackage{geometry}

% Set up page geometry
\geometry{a4paper, margin=1in}

% Header and Footer settings
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyhead[C]{Healing Songs and their Meanings} % Header center
\fancyfoot[L]{Maulana Abul Kalam Azad University of Technology} % Footer left
\fancyfoot[R]{\thepage} % Footer right (page number)

\begin{document}

% Title of the document
\title{Healing Songs and their Meanings}
\author{}
\date{}

\maketitle

% Restore fancy page style after the title page
\thispagestyle{fancy}
\pagestyle{fancy}

% Section 1
\section{Kidult}
The song "Kidult" by SEVENTEEN is a reflection of bittersweet feelings one experiences being in adulthood-that is to say, try to live life carefree and whimsical like childhood while at the same time shoulder responsibilities and trouble of growing into adulthood. That is very well captured in the hybrid word "Kidult," in the sense that these four letters mutate into "kid" and "adult." Then, the lyrics also include yearning for the innocence and freedom of youthful years accompanied by the inevitable reality of moving into adulthood. Despite all the struggles and strain of being mature, the song urges one to be a child within themselves and hug the minute pleasures that still remain. And, most importantly, reminds one that it is okay to hold onto being a kid with his dreams and emotions in adult life.

% Section 2
\section{Circles}
The song "Circles" by SEVENTEEN is a song that was full of repetition, healing, and emotional growth. In this line, I captured the very essence of lifecycles: sometimes people repeat themselves, but in other instances, with time, the same struggle appears to be similar or repeating. However, whereas getting trapped in these types of circles is a common phenomenon, the song grasped the strength found within them. It's a song of hope, urging people to embrace their journey and trust that, no matter how things repeat or seem grueling, they are indeed slowly moving forward. With all the ups and downs, "Circles" reminds us that healing takes time and every loop in life helps us grow stronger and more resilient.
 
\end{document}



